Figures

### 2019-07-18 figures/07_model-selection.Rmd
fix label

gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = as.numeric(fit_tp$re_global["50%"])) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TP model, pasture RE slope") + xlab("Zone ID") +
  theme(legend.position = 0)

>>>>

gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = as.numeric(fit_tp$re_global["50%"])) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TP model, Ag RE slope") + xlab("Zone ID") +
  theme(legend.position = 0)
